Local connections

### 2023-09-21 notebook/analysis-local.qmd
Add fuzzy stacked bar chart for local connections

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_local))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))

@@

```{r plot-epred-local}
epreds <- m_full_ordbeta |> 
  epred_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
              ndraws = 1000)

epreds |> 
  ungroup() |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  ggplot(aes(x = .epred, y = local_connect)) +
  stat_halfeye(fill = clrs[2]) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

```{r plot-pred-discrete-continuous-local, message=FALSE}
preds_local_plot <- preds_local |> 
  unnest(preds) |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, local_connect, draw) |> 
  summarize(count = n()) |> 
  group_by(local_connect) |> 
  mutate(prop = count / sum(count) * 100)

ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
  stat_pointinterval(color = clrs[2]) +
  expand_limits(y = 0) +
  facet_wrap(vars(outcome)) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(labels = label_percent()) +
  labs(x = NULL, y = "Proportion of predictions") +
  theme_ongo()
```

>>>>

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_local, epreds_local))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()

@@

```{r plot-epred-local}
epreds_local |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  ggplot(aes(x = .epred, y = local_connect)) +
  stat_halfeye(fill = clrs[2]) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(0, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL) +
  coord_cartesian(xlim = c(0, 1)) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

```{r plot-pred-discrete-continuous-local-bars, message=FALSE, fig.width=4.5, fig.height=3.5, out.width="60%"}
preds_local_plot <- preds_local |> 
  unnest(preds) |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  group_by(outcome, local_connect, draw) |> 
  summarize(count = n()) |> 
  group_by(local_connect, draw) |> 
  mutate(prop = count / sum(count))

preds_local_text <- preds_local_plot |> 
  group_by(outcome, local_connect) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  group_by(local_connect) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  ))

preds_local_plot |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = position_stack(), linewidth = 0, width = 1) +
  geom_text(
    data = preds_local_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
  labs(x = NULL, y = "Proportion of predictions", fill = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )
```
